Twisted 11-dimensional supergravity

### 2021-10-14 dimred.tex
merge refs

\subsection{Kodaira--Spencer theory}

@@

\parsec[s:poisson]
The original action for Kodaira-Spencer theory posited by \cite{BCOV}\surya{which reference is BCOV} has a nonlocal kinetic term. In the BV formalism, this is codified by stipulating that the BV pairing is a degenerate odd Poisson tensor rather than an odd symplectic form. The Poisson kernel is given by the expression 
\[
(\div\otimes 1)\delta_{\Delta \subset X\times X} \in \Sym^2 (\PV^{\bu,\bu}(X)[[u]][2])
.\]
Explicitly, the above kernel pairs against the dual to 
\[
\Sigma^1 = \sum u^k\mu^1_k, \Sigma^2 = \sum u^k\mu^2_k\in \PV^{\bu,\bu}(X)[[u]][2]
\]
 by the formula 
\[
\int \overline{\mu}_0^1\div \overline{\mu}_0^2.
\] 
Here, the overlines denote the dual field in 
\[
(\PV^{\bu,\bu}(X)[[u]][2])^*=\PV_c^{d-\bu,d-\bu}(X)[[u]][2].
\] 
That is, further expanding the fields as 
\[
\mu_k = \sum_{i,j=1}^d\mu_k^{(i,j)}\in \PV^{i,j}
\] 
the expression pairs $\overline{\mu}_0^{(i,j)}$ with $\overline{\mu}_0^{(d-1-i, d-j)}$.

@@

There is a natural local interaction which equips the above cyclic cochain complex with the structure of $\Z/2$ graded Poisson BV theory. Explicitly, it is given by 
\beqn
I_{BCOV}(\Sigma) = \int^\Omega \langle \exp \Sigma\rangle_0 = \sum_{n\geq 0} \int^\Omega\langle\Sigma^{\otimes n}\rangle_0
\eeqn

where $\langle - \rangle_0$ denotes the genus zero Gromov-Witten invariant with marked points
\beqn
\langle u^{k_1}\mu_1 \otimes \cdots \otimes u^{k_m}\mu_m\rangle_0 := \left (\int _{\overline {\cM}_{0,m}} \psi_1^{k_1}\cdots \psi_m^{k_m}\right ) \mu_1\cdots \mu_m = \binom{m-3}{ k_1,\cdots, k_m}  \mu_1\cdots \mu_m.
\eeqn

@@

In \cite{BCOV} the authors show that the above interaction satisfies the classical master equation. Moreover, they show that the $L_\infty$ structure determined by the above action is equivalent to a natural dgla structure on the complex of fields with Lie bracket given by the Schouten bracket. Explicitly, the equivalence is given by the transcendental automorphism 
\[
\Sigma \mapsto [u(\exp (\Sigma/u)-1)]_+
\]
where $[-]_+$ denotes projection onto positive powers of $u$.
\parsec[s:minimalks]

Recall we observed in \ref[s:poisson] that the majority of fields pair to zero under the Poisson tensor. Physically these correspond to closed string fields that do not propogate. In the supergravity approximation, the fields that survive are those closed string fields that propogate. In terms of our description of closed string field theory in terms of Kodaira-Spencer theory, this motivates us to consider the smallest cochain complex containing those fields thathave nonzero pairing under the Poisson tensor. This is referred to as minimal Kodaira-Spencer theory.

The fields of minimal Kodaira-Spencer theory are given by the subcomplex of \label{eqn:ks1}
\beqn
\left (\bigoplus_{i+j\leq d -1}u^i\PV^{j,\bu}(X)[2], \dbar + u \div\right).
\eeqn
 It is easy to see that there is a natural odd Poisson tensor on the above cochain complex such that the inclusion of this subcomplex into the fields of Kodaira-Spencer theory is a Poisson map. There is a natural action functional given by pulling back the Kodaira-Spencer action.

@@

We recall the description of the $SU(4)$ twist of type IIA supergravity conjectured in \cite{CLsugra}. 
In principal, there is also a minimal, $SU(5)$ invariant, twist of type IIA supergravity but so far no description, even conjecturally, exists.
We turn to this in Section \ref{sec:SU(5)twistIIA}.

Let $X$ be a Calabi-Yau manifold of complex dimension four. 
The complex of fields of minimal Kodaira--Spencer theory on $X$ takes the form
\brian{I have an issue with how this is organized}
\beqn
\begin{tikzcd}
                        &                          &                                     & {\PV^{0,\bu}}    \\
                        &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
                        & {\PV^{2,\bu}} \arrow[r, "u\div"]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
{\PV^{3,\bu}} \arrow[r, "u\div"] & {u\PV^{2,\bu}} \arrow[r, "u\div"] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
\end{tikzcd}.
\eeqn
Denote this complex by $\cE_{mKS}(X)$. 
The classical BCOV action $I_{BCOV}$ follows from the general formula we gave above.

With this in hand the conjecture of \cite{CLSugra} takes the following form.

@@

Recall that in the physical theory, the components of the $C$-field in 11d that are not supported along the M-theory circle become the components of the Ramond--Ramond 2-form of type IIA. However, as noted in \cite{CLSugra} components of Ramond--Ramond fields do not appear as fields in Kodaira--Spencer theory; rather it is components of their field strengths that appear. Since components of the $C$-field become components of $\gamma_{11d}$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.

@@

Recall that the original fields of the IIA supergravity model on $\CC^4 \times \RR^2$ was equipped with an odd Poisson bivector which was degenerate.
In other words, it did not define a theory in the conventional BV formalism. 
One of the key features of this new complex of fields, after we have taken these potentials, is that it is equipped with an odd non-degenerate pairing thus equipping it with the structure of a theory in the conventional BV formalism.

The pairing is $\Res_u \frac{\d u}{u} \int^\Omega_{\CC^4 \times \RR^2} \alpha \vee \alpha'$ where $\alpha, \alpha'$ are two general fields in this potential theory on $\CC^4 \times \RR^2$. 
Explicitly, in the description of the fields in \eqref{eqn:IIApot} the pairing is 
\[
\int^\Omega_{\CC^4 \times \RR^2} \eta \theta + \int^\Omega_{\CC^4 \times \RR^2} \mu \vee \gamma + \int^\Omega_{\CC^4 \times \RR^2} \nu \beta .
\]
This pairing is compatible with the odd Poisson bracket present in the original theory on $\CC^4 \times \RR^2$. \brian{finish}

@@

The action is
\begin{multline}
\label{eqn:5daction} 
\int^\Omega_{\CC^2 \times \RR} \left(\eta \dbar \alpha + B_{grav} \dbar A_{grav} + B \dbar A + \psi \dbar \chi \right) \\
  \int^\Omega_{\CC^2 \times \RR} \left( \frac12\eta \{\alpha, \alpha\} +  B_{grav} \{\alpha, A_{grav}\}+ B \{\alpha, A\} +  \psi \{\alpha, \chi \}\right) \\ 
+ \frac16 \int_{\CC^2 \times \RR} B_{grav} \del B_{grav} \del B_{grav} .
\end{multline}
\end{conj}

@@

First, we set up some notation. 
Let $\Omega_X$ be the holomorphic volume form on $X$. 
To define the $11$-dimensional theory on $X \times \CC^2 \times \RR$ we use the Calabi--Yau form $\Omega_X \wedge \d z_1 \wedge \d z_2$, where $\{z_i\}$ is a holomorphic coordinate on $\CC^2$. 
Let $\omega \in \Omega^{1,1}(X)$ be a fixed K\"ahler form on $X$.
For any $k$, let $H^k(X, \Omega^k_X)_\perp$ denote the cohomology of the primitive elements. 
\brian{good notation?}

@@

We obtain further evidence that this is the $SU(5)$ invariant twist of type IIA supergravity by checking that it has the expected residual supersymmetries. 
The type IIA superstring algebra $\lie{string}_{IIA}$ is a central extension of the 10d $\cN=(1,1)$ super Poincar\'e algebra, for a definition we refer to \cite{BH,FSS}.

A minimal twisting supercharge $Q_{hol}$ in the $\cN=(1,1)$ super Poincar\'e algebra determines a maximal isotropic $L \subset \CC^{10}$. 
In a completely analogous way to the calculation for the twist of the algebra $\m2$ or the $SU(4)$ twist of the as in \cite{CLsugra} one can prove the following.

\begin{prop}
As an $\lie{sl}(5)$ representation the $Q_{hol}$-cohomology of $\lie{string}_{IIA}$ is equivalent

>>>>

\subsection{Kodaira--Spencer theory}
\label{s:BCOV}

@@

\parsec[s:poisson]
The original action for Kodaira-Spencer theory posited by \cite{BCOV}\surya{which reference is BCOV} has a nonlocal kinetic term. In the BV formalism, this is codified by stipulating that the BV pairing is a degenerate odd Poisson tensor rather than an odd symplectic form. 
The Poisson kernel is given by the expression 
\[
(\div\otimes 1)\delta_{\Delta \subset X\times X} \in \left[\PV^{\bu,\bu}(X)\right]^{\hotimes 2} ,
\]
see \cite[{\S 1.4}]{CLbcov1}. 
Here, we view the $\delta$-distribution as a polyvector field using the Calabi--Yau form. 
Notice that the shifted Poisson tensor does not involve the parameter $u$ at all. 
For this reason, only the duals of a small number of fields pair nontrivially under the resulting odd BV bracket. 
%Explicitly, the above kernel pairs against the dual to 
%\[
%\Sigma^1 = \sum u^k\mu^1_k, \Sigma^2 = \sum u^k\mu^2_k\in \PV^{\bu,\bu}%(X)[[u]][2]
%\]
% by the formula 
%\[
%\int \overline{\mu}_0^1\div \overline{\mu}_0^2.
%\] 
%Here, the overlines denote the dual field in 
%\[
%(\PV^{\bu,\bu}(X)[[u]][2])^*=\PV_c^{d-\bu,d-\bu}(X)[[u]][2].
%\] 
%That is, further expanding the fields as 
%\[
%\mu_k = \sum_{i,j=1}^d\mu_k^{(i,j)}\in \PV^{i,j}
%\] 
%the expression pairs $\overline{\mu}_0^{(i,j)}$ with $\overline{\mu}_0^{(d-1-i, d-j)}$.

@@

There is a natural local interaction which equips the complex \eqref{eqn:ks1} with the structure of $\Z/2$ graded Poisson BV theory. Explicitly, it is given by 
\beqn
I_{BCOV}(\Sigma) = {\rm Tr}_X \, \langle \exp \Sigma\rangle_0 = \sum_{n\geq 0} {\rm Tr}_X \, \langle\Sigma^{\otimes n}\rangle_0
\eeqn
where ${\rm Tr}_X \, \Phi = \int_X (\Phi \vee \Omega) \wedge \Omega$ and where $\langle - \rangle_0$ denotes the genus zero Gromov-Witten invariant with marked points
\beqn
\langle u^{k_1}\mu_1 \otimes \cdots \otimes u^{k_m}\mu_m\rangle_0 := \left (\int _{\overline {\cM}_{0,m}} \psi_1^{k_1}\cdots \psi_m^{k_m}\right ) \mu_1\cdots \mu_m = \binom{m-3}{ k_1,\cdots, k_m}  \mu_1\cdots \mu_m.
\eeqn

@@

In \cite{BCOV} the authors show that the above interaction satisfies the classical master equation. Moreover, they show that the $L_\infty$ structure determined by the above action is equivalent to a natural dgla structure on the complex of fields with Lie bracket given by the Schouten bracket. Explicitly, the equivalence is given by the transcendental automorphism 
\[
\Sigma \mapsto [u(\exp (\Sigma/u)-1)]_+
\]
where $[-]_+$ denotes projection onto positive powers of $u$.

\parsec[s:minimalks]

We pointed out in \S\ref{s:poisson} that the majority of fields pair to zero under the Poisson tensor. Physically these correspond to closed string fields that do not propogate. In the supergravity approximation, the fields that survive are those closed string fields that propogate. In terms of our description of closed string field theory in terms of Kodaira-Spencer theory, this motivates us to consider the smallest cochain complex containing those fields thathave nonzero pairing under the Poisson tensor. This is referred to as minimal Kodaira-Spencer theory.

The fields of minimal Kodaira-Spencer theory are given by the subcomplex of \label{eqn:ks1}
\beqn
\left (\bigoplus_{i+j\leq d -1}u^i\PV^{j,\bu}(X)[2], \dbar + u \div\right).
\eeqn
We observe that the original odd Poisson tensor lives in this subcomplex. 
%here is a natural odd Poisson tensor on the above cochain complex such that the inclusion of this subcomplex into the fields of Kodaira-Spencer theory is a Poisson map. 
There is a natural action functional given by restricting $I_{BCOV}$ to this space.

@@

We recall the description of the $SU(4)$ twist of type IIA supergravity conjectured in \cite{CLsugra}. 
In principal, there is also a minimal, $SU(5)$ invariant, twist of type IIA supergravity but so far no description, even conjecturally, exists.
We turn to this in \S \ref{s:su5IIA}.

Let $X$ be a Calabi-Yau manifold of complex dimension four. 
The $\ZZ/2$ graded complex of fields of minimal Kodaira--Spencer theory on $X$ takes the form
\beqn
\begin{tikzcd}
                        &                          &                                     & {\PV^{0,\bu}}    \\
                        &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
                        & {\PV^{2,\bu}} \arrow[r, "u\div"]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
{\PV^{3,\bu}} \arrow[r, "u\div"] & {u\PV^{2,\bu}} \arrow[r, "u\div"] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
\end{tikzcd}.
\eeqn
Here, $u^\ell\PV^{k,i}$ is placed in parity $k + i -1 \mod 2$. 
%Denote this complex by $\cE_{mKS}(X)$. 
The classical BCOV action $I_{BCOV}$ follows from the general formula we gave above.

With this in hand the conjecture of \cite{CLsugra} takes the following form.

@@

Recall that in the physical theory, the components of the $C$-field in 11d that are not supported along the M-theory circle become the components of the Ramond--Ramond 2-form of type IIA. However, as noted in \cite{CLsugra} components of Ramond--Ramond fields do not appear as fields in Kodaira--Spencer theory; rather it is components of their field strengths that appear. Since components of the $C$-field become components of $\gamma_{11d}$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.

@@

The original space of fields of the twist of IIA supergravity on $\CC^4 \times \RR^2$ was equipped with an odd Poisson bivector which was degenerate.
In other words, it did not define a theory in the conventional BV formalism. 
One of the key features of this new complex of fields, after we have taken these potentials, is that it is equipped with an odd non-degenerate pairing thus equipping it with the structure of a theory in the conventional BV formalism.

The pairing is $\Res_u \frac{\d u}{u} \int^\Omega_{\CC^4 \times \RR^2} \alpha \vee \alpha'$ where $\alpha, \alpha'$ are two general fields in this potential theory on $\CC^4 \times \RR^2$. 
Explicitly, in the description of the fields in \eqref{eqn:IIApot} the pairing is 
\[
\int^\Omega_{\CC^4 \times \RR^2} \eta \theta + \int^\Omega_{\CC^4 \times \RR^2} \mu \vee \gamma + \int^\Omega_{\CC^4 \times \RR^2} \nu \beta .
\]
This pairing is compatible with the odd Poisson bracket present in the original theory on $\CC^4 \times \RR^2$.

@@

The action is
\begin{multline}
\label{eqn:5daction} 
\int^\Omega_{\CC^2 \times \RR} \left(\eta \dbar \alpha + B_{grav} \dbar A_{grav} + B \dbar A + \psi \dbar \chi \right) \\
  + \int^\Omega_{\CC^2 \times \RR} \left( \frac12\eta \{\alpha, \alpha\} +  B_{grav} \{\alpha, A_{grav}\}+ B \{\alpha, A\} +  \psi \{\alpha, \chi \}\right) \\ 
+ \frac16 \int_{\CC^2 \times \RR} B_{grav} \del B_{grav} \del B_{grav} .
\end{multline}
\end{conj}

@@

First, we set up some notation. 
Let $\Omega_X$ be the holomorphic volume form on $X$. 
To define the $11$-dimensional theory on $X \times \CC^2 \times \RR$ we use the Calabi--Yau form $\Omega_X \wedge \d z_1 \wedge \d z_2$, where $\{z_i\}$ is a holomorphic coordinate on $\CC^2$. 
Let $\omega \in \Omega^{1,1}(X)$ be a fixed K\"ahler form on $X$.
For any $k$, let $H^k(X, \Omega^k_X)_\perp$ denote the cohomology of the primitive elements.

@@

%\parsec[]
%
%
%We obtain further evidence that this is the $SU(5)$ invariant twist of type IIA supergravity by checking that it has the expected residual supersymmetries. 
%The type IIA superstring algebra $\lie{string}_{IIA}$ is a central extension of the 10d $\cN=(1,1)$ super Poincar\'e algebra, for a definition we refer to \cite{BH,FSS}. 
%
%A minimal twisting supercharge $Q_{hol}$ in the $\cN=(1,1)$ super Poincar\'e algebra determines a maximal isotropic $L \subset \CC^{10}$. 
%In a completely analogous way to the calculation for the twist of the algebra $\m2$ or the $SU(4)$ twist of the as in \cite{CLsugra} one can prove the following. 
%
%\begin{prop}
%As an $\lie{sl}(5)$ representation the $Q_{hol}$-cohomology of $\lie{string}_{IIA}$ is equivalent
%\end{prop}

### 2021-10-14 intro.tex
merge refs

In \cite{SWspinor}, the last two authors used the formalism of pure spinors to describe the {\em free field limit} of the minimal twist of 11-dimensional supergravity on flat space.
The resulting theory is $\ZZ/2$ graded which is inherited from the ghost grading and parity in the original, untwisted, 11-dimensional theory.
In \S\ref{sec:dfn} we extend this free limit of the twist of 11-dimensional supergravity to a fully interacting theory in the Batalin--Vilkovisky (BV) formalism.\footnote{One subtlety is that unlike the usual BV formalism which involves a $\ZZ$-grading by ghost number, the 11-dimensional theory is only $\ZZ/2$ graded.
All odd fields can therefore be considered as ``ghosts'' in the twisted theory.}
Our main conjecture is that this interacting BV theory is equivalent to the minimal twist of 11-dimensional supergravity on flat space.

@@

Our 11-dimensional theory is defined more generally on the product of manifolds 
\[
X \times L
\]
where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented real one-dimensional manifold. 
The theory is of a holomorphic gravitational flavor as it describes ``partial'' deformations of complex structures along $X$. 
We will explain what we mean by this momentarily.

In our theory there is a field which encodes this partial deformation of complex structure on the Calabi--Yau manifold $X$.
It is an even field 
\[
\mu \in \Omega^{0,1} (X , \T_X) \otimes C^\infty(L) 
\]
where $\T_X$ denotes the holomorphic tangent bundle on $X$.
Locally, $\mu$ can be decomposed as Beltrami-like differential
\[
\mu = \mu^i_j (z,\zbar, t) \d \zbar_i \frac{\partial}{\partial z_j} .
\]
Physically speaking, $\mu$ is a component of the metric which survives in the twisted theory, see \S \ref{s:component}.

Next, there are two fields 
\[
\gamma^{1,0} \in \Omega^{1,0} (X) \otimes C^\infty(L), \quad \gamma^{1,2} \in \Omega^{1,2}(X) \otimes C^\infty(L) .
\]
The field $\gamma^{1,2}$ is a component of the supergravity $3$-form $C$-field that survives in the twisted theory. 
The field $\gamma^{1,0}$ can be interpreted as a component of the one-form which is a ghost-for-a-ghost of the $C$-field.\footnote{The $C$-field has a gauge symmetry of the form $\delta C = \d B$ where $B$ is a two-form.
This ghost $B$ field has an additional gauge symmetry $\delta B = \d A$ for $A$ a one-form.
The field $\gamma^{1,0}$ is a component of $A$.}

There is a background where the equations of motion involving the $\mu, \gamma^{1,0}, \gamma^{1,2}$ fields in our 11-dimensional theory read
\begin{align*}
\dbar \mu + \frac12 [\mu, \mu] + \Omega^{-1} \vee \left(\del \gamma^{1,0} \wedge \del \gamma^{1,2} \right) & = 0 \\
(\dbar + \mu) \gamma^{1,0} = 
(\dbar + \mu) \gamma^{1,2} & = 0 \\
\div \mu & = 0 \\
\d_L \mu = \d_L \gamma^{1,0} = \d_L \gamma^{1,2} = & = 0 .
\end{align*}
In the last line $\d_L$ is the de Rham differential on $L$ and implies that $\mu, \gamma^{1,0}$, and $\gamma^{1,2}$ are locally constant along $L$. 
Notice that were it not for the presence of the last term in the first equation then this would be the integrability equation for $\mu$ to determines a complex structure on $X$.
The second two equations resemble the conditions that $\gamma^{1,0}, \gamma^{1,2}$ be holomorphic with the complex structure determined by $\mu$. 
Finally, the fourth equation constrains $\mu$ to preserve the holomorphic volume form on $X$.

If we work in a background where one of $\gamma^{1,0}$ or $\gamma^{1,2}$ is zero then we see that $\mu$ is exactly a deformation of complex structure along $X$. 
In terms of the 11-dimensional geometry, this is a background which describes deformations of the natural transverse holomorphic foliation (THF structure) on $X \times L$ which further preserves the holomorphic volume form along the leaves.
We further unpack the equations of motion in other backgrounds in \S \ref{s:eom}.
%The equations of motion state that $\gamma$ is constant along $\RR$ and holomorphic along $\CC^5$. 
%Further, $\gamma$ is only defined up to the additional of a total holomorphic derivative $\gamma \sim \gamma + \del \beta$ where $\beta$ is a holomorphic function on $\CC^5$ which is constant along $\RR$.

@@

Given our main conjecture that the interacting 11-dimensional BV theory on $\CC^5 \times \RR$ is the twist of supergravity, we obtain the following.

>>>>

In \cite{SWspinor}, the last two authors used the formalism of pure spinors to describe the {\em free field limit} of the minimal twist of 11-dimensional supergravity on flat space.
\brian{also reference fabian and richard}
The resulting theory is $\ZZ/2$ graded which is inherited from the ghost grading and parity in the original, untwisted, 11-dimensional theory.
In \S\ref{sec:dfn} we extend this free limit of the twist of 11-dimensional supergravity to a fully interacting theory in the Batalin--Vilkovisky (BV) formalism.\footnote{One subtlety is that unlike the usual BV formalism which involves a $\ZZ$-grading by ghost number, the 11-dimensional theory is only $\ZZ/2$ graded.
All odd fields can therefore be considered as ``ghosts'' in the twisted theory.}
Our main conjecture is that this interacting BV theory is equivalent to the minimal twist of 11-dimensional supergravity on flat space.

@@

Our 11-dimensional theory is defined more generally on the product of manifolds 
\[
X \times S
\]
where $X$ is a Calabi--Yau five-fold and $S$ is a smooth oriented real one-dimensional manifold. 
The theory is of a holomorphic gravitational flavor as it describes ``partial'' deformations of complex structures along $X$. 
We will explain what we mean by this momentarily.

In our theory there is a field which encodes this partial deformation of complex structure on the Calabi--Yau manifold $X$.
It is an even field 
\[
\mu \in \Omega^{0,1} (X , \T_X) \otimes C^\infty(S) 
\]
where $\T_X$ denotes the holomorphic tangent bundle on $X$.
Locally, $\mu$ can be decomposed as Beltrami-like differential
\[
\mu = \mu^i_j (z,\zbar, t) \d \zbar_i \frac{\partial}{\partial z_j} .
\]
Physically speaking, $\mu$ is a component of the metric which survives in the twisted theory, see \S \ref{s:component}.

Next, there are two fields 
\[
\gamma^{1,0} \in \Omega^{1,0} (X) \otimes C^\infty(S), \quad \gamma^{1,2} \in \Omega^{1,2}(X) \otimes C^\infty(S) .
\]
The field $\gamma^{1,2}$ is a component of the supergravity $3$-form $C$-field that survives in the twisted theory. 
The field $\gamma^{1,0}$ can be interpreted as a component of the one-form which is a ghost-for-a-ghost of the $C$-field.\footnote{The $C$-field has a gauge symmetry of the form $\delta C = \d B$ where $B$ is a two-form.
This ghost $B$ field has an additional gauge symmetry $\delta B = \d A$ for $A$ a one-form.
The field $\gamma^{1,0}$ is a component of $A$.}

There is a background where the equation of motion involving the $\mu, \gamma^{1,0}, \gamma^{1,2}$ fields reads
\begin{align*}
\dbar \mu + \frac12 [\mu, \mu] + \Omega^{-1} \vee \left(\del \gamma^{1,0} \wedge \del \gamma^{1,2} \right) & = 0 \\
%(\dbar + \mu) \gamma^{1,0} = 
%(\dbar + \mu) \gamma^{1,2} & = 0 
%\\
%\div \mu & = 0 \\
%\d_S \mu = \d_S \gamma^{1,0} = \d_S \gamma^{1,2} = & = 0 .
\end{align*}
Additionally, there are the conditions that $\mu$ preserve the holomorphic volume form on $X$ and that all fields are locally constant along the topological direction $S$.  
%In the last line $\d_S$ is the de Rham differential on $L$ and implies that $\mu, \gamma^{1,0}$, and $\gamma^{1,2}$ are locally constant along $L$. 
Notice that were it not for the presence of the last term in the first equation then this would be the integrability equation for $\mu$ to determines a complex structure on $X$.
%The second two equations resemble the conditions that $\gamma^{1,0}, \gamma^{1,2}$ be holomorphic with the complex structure determined by $\mu$. 
%Finally, the fourth equation constrains $\mu$ to preserve the holomorphic volume form on $X$.

If we work in a background where one of $\gamma^{1,0}$ or $\gamma^{1,2}$ is zero then we see that $\mu$ is exactly a deformation of complex structure along $X$. 
In terms of the 11-dimensional geometry, this is a background which describes deformations of the natural transverse holomorphic foliation (THF structure) on $X \times S$ which further preserves the holomorphic volume form along the leaves.
We further unpack the equations of motion in other backgrounds in \S \ref{s:eom}.
%The equations of motion state that $\gamma$ is constant along $\RR$ and holomorphic along $\CC^5$. 
%Further, $\gamma$ is only defined up to the additional of a total holomorphic derivative $\gamma \sim \gamma + \del \beta$ where $\beta$ is a holomorphic function on $\CC^5$ which is constant along $\RR$.

@@

In particular, correlation functions involving observables of the 11-dimensional theory will be constrained by the infinite-dimensional symmetry algebra $E(5,10)$. 
Given our main conjecture that the interacting 11-dimensional BV theory on $\CC^5 \times \RR$ is the twist of supergravity, we obtain the following.

### 2021-10-14 matrix.tex
merge refs

Our main result is to relate the global symmetry algebra of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional super Lie algebra studied by Kac \cite{KacClass,KR} called $E(5,10)$.
We recall the definition below.

>>>>

Our main result is to relate the global symmetry algebra of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional super Lie algebra studied by Kac \cite{KacBible,KacE510} called $E(5,10)$.
We recall the definition below.
